Supporting online material for\\ \emph{Effectiveness of UNAIDS targets and HIV vaccination across 127 countries}

### 2016-08-15 Documents/supplementary_text.tex
Working on supplementary figures.

\usepackage{amsmath}
\usepackage{geometry}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage[utf8x]{inputenc}
\usepackage{microtype}
\usepackage[final]{pdfpages}
\usepackage{float}
\usepackage{longtable}
\usepackage[labelsep = period, singlelinecheck = off, labelfont = {bf}]{caption}

% Load hyperref after the other stuff above.
\usepackage[pdfborder={0 0 0}]{hyperref}
\usepackage[numbers,round,sort&compress]{natbib}
\usepackage{hypernat}

@@

\section*{To do}

\begin{itemize}
\item Finish tables
\item Reformat transmission rate figure
\end{itemize}

@@

The source code for the model and analysis tools is available at
\url{https://github.com/janmedlock/HIV-95-vaccine/}.

@@

Several sources provided information to parameterize our model at the
country level. Demographic data, including population growth rate
\cite{WorldBankpg}, death rate
\cite{World_Development_Indicators2013-ee}, and number of people aged
15--49 years \cite{The_World_Bank2016-fd} were obtained from the World
Bank. Longitudinal HIV incidence and prevalence estimates for the
15--49 age group, spanning from as early as 1990 to 2015, was
primarily derived from the AIDSinfo database produced by UNAIDS
\cite{Unaids2016-an}. Other sources included UNAIDS Country Progress
Reports \cite{Unaids2016-am} published from 2012 to 2016 and AIDS Data
Hub \cite{AIDSdatahub-fg}, which compiles data from UNAIDS, UNICEF,
WHO, and the Asian Development Bank. These sources were also used to
inform the initial conditions for the model: the number of people who
have been diagnosed with HIV, who are on ART, and who have viral
suppression or have been retained on treatment for at least 12
months. Where data were not available from these sources, alternative
resources such as peer-reviewed journal articles and country health
ministry reports were consulted.  We found sufficient data to
parametrize our mathematical modeling for 127 countries.  See
Supplemental data files for full information on data sources for each
country.

@@

\begin{figure}
  \centering
  \includegraphics{../Codes/plots/transmission_rate}
  \caption{Country-specific transmission rates were calculated based
    on the relative contributions of individuals with acute infection,
    unsuppressed viral load or suppressed viral load to overall
    transmission (\autoref{model_fitting}). The estimates were
    calibrated to data on country-level incidence and/or prevalence to
    account for variation in historical incidence while accurately
    reflecting recent HIV rates.}
  \label{transmission_rate}
\end{figure}

@@

\bibliographystyle{science_nat}

\bibliography{supplementary_text}

\appendix
\clearpage
\section{Model results by region and country}

\input{../Codes/plots/effectiveness_all/all}

>>>>

\usepackage{amsmath}
\usepackage{geometry}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage[utf8x]{inputenc}
\usepackage{microtype}
\usepackage[font = {sf}, labelfont = {bf},
  labelsep = period, singlelinecheck = off]{caption}
\usepackage[font = {sf}]{floatrow}

% Load hyperref after the other stuff above.
\usepackage[pdfborder={0 0 0}]{hyperref}
\usepackage[numbers, round, sort&compress]{natbib}
\usepackage{hypernat}

@@

@@

The source code for the model and analysis tools is publicly available
at \url{https://github.com/janmedlock/HIV-95-vaccine/}
\cite{medlock2016-git}.

@@

Several sources provided information to parameterize our model at the
country level. Demographic data, including population growth rate
\cite{WorldBankpg}, death rate
\cite{World_Development_Indicators2013-ee}, and number of people aged
15--49 years \cite{The_World_Bank2016-fd} were obtained from the World
Bank. Longitudinal HIV incidence and prevalence estimates for the
15--49 age group, spanning from as early as 1990 to 2015, was
primarily derived from the AIDSinfo database produced by UNAIDS
\cite{Unaids2016-an}. Other sources included UNAIDS Country Progress
Reports \cite{Unaids2016-am} published from 2012 to 2016 and AIDS Data
Hub \cite{AIDSdatahub-fg}, which compiles data from UNAIDS, UNICEF,
WHO, and the Asian Development Bank. These sources were also used to
inform the initial conditions for the model: the number of people who
have been diagnosed with HIV, who are on ART, and who have viral
suppression or have been retained on treatment for at least 12
months. Where data were not available from these sources, alternative
resources such as peer-reviewed journal articles and country health
ministry reports were consulted.  We found sufficient data to
parametrize our mathematical modeling for 127 countries.  See
Supplemental data files for full information on data sources for each
country.  The data files are also available in the public source-code
repository \cite{medlock2016-git}.

@@

\begin{figure}
  \centering
  \includegraphics{../Codes/plots/transmission_rate.pdf}
  \caption{Country-specific transmission rates were calculated based
    on the relative contributions of individuals with acute infection,
    unsuppressed viral load or suppressed viral load to overall
    transmission (\autoref{model_fitting}). The estimates were
    calibrated to data on country-level incidence and/or prevalence to
    account for variation in historical incidence while accurately
    reflecting recent HIV rates.}
  \label{transmission_rate}
\end{figure}

@@

\clearpage
\bibliographystyle{science_nat}
\bibliography{supplementary_text}

\appendix
\newpage
\vspace*{3in}
\section{Model results by region and country}
\newpage
\input{../Codes/plots/effectiveness_all/all}
